---
title: "Shiny App Pitch - Air Quality dataset exploratory analysis"
subtitle: "Presentation of shiny app developed for the course project of the Developing Data Products course"
author: "Ilda Dreoni"
date: "26/09/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Synposis
========================================================

This applications allows the user to explore the Air Quality Dataset from the datasets package.

Capabilities

- Plotting histograms of main variables of interest
- Plot scatter plot and linear regression lines

The Dataset
========================================================

The app uses airquality dataset available in base package in R.

This is a data set collected and used to measure the air quality in New York State.

Information about the dataset:

```{r}
data(airquality)
head(airquality)
```


The variables
========================================================
The application analyses the following variables:

* Ozone
* Solar Radiation
* Wind

In the first tab plots the histograms of the three variables and allow the user to choose the number of bins

In the second tab it plots the Wind and Solar Radiation against Ozone values and it fits a linear regression model. The user can select for which month to estimate the model and whether include all points or exclude the more extreme.

Shiny Air Pollution App
========================================================

Shiny https://ildadreoni.shinyapps.io/AirQuality_app/

GitHub https://github.com/idreoni/ShinyApplication